API design for machine learning software: experiences from the scikit-learn project

### 2013-06-27 paper.tex
Non-proliferation of classes: less intimidating phrasing
s/fold/integrate/ in meta-estimators (@amueller was confused :)

\begin{description}
  \item[Consistency.]
       All objects (basic or composite) share a consistent interface composed of
       a limited set of methods. This interface is documented in a consistent
       manner for all objects.
  \item[Inspection.]
       Constructor parameters and parameter values determined by learning
       algorithms are stored and exposed as public attributes.
  \item[Non-proliferation of classes.]
       Learning algorithms are the only objects to be of custom classes.
       Datasets and hyper-parameter names and values are represented as standard
       Python, NumPy or SciPy classes rather than new ones whenever possible.
       This keeps \sklearn easy to use and easy to combine with other libraries.
  \item[Composition.]
       Many machine learning tasks are expressible
       as sequences or combinations of transformations to data.
       Some learning algorithms are also naturally viewed
       as meta-algorithms parametrized on other algorithms.
       Whenever feasible, such algorithms are implemented and composed from
       existing building blocks.
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       an appropriate default value is defined by the library.
       The default value should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}

@@

Since meta-estimators require users to construct nested objects,
the decision to implement a meta-estimator
rather than fold the behavior it implements
into existing estimators classes
is always based on a trade-off between generality and ease of use.
Relating to the example just given,
all \sklearn classifiers are designed to do multiclass classification
and the use of the \texttt{multiclass} module
is only necessary in advanced use cases.

>>>>

\begin{description}
  \item[Consistency.]
       All objects (basic or composite) share a consistent interface composed of
       a limited set of methods. This interface is documented in a consistent
       manner for all objects.
  \item[Inspection.]
       Constructor parameters and parameter values determined by learning
       algorithms are stored and exposed as public attributes.
  \item[Non-proliferation of classes.]
       Learning algorithms are the only objects to be of custom classes.
       Datasets and hyper-parameter names and values are represented as standard
       Python, NumPy or SciPy objects whenever possible.
       This keeps \sklearn easy to use and easy to combine with other libraries.
  \item[Composition.]
       Many machine learning tasks are expressible
       as sequences or combinations of transformations to data.
       Some learning algorithms are also naturally viewed
       as meta-algorithms parametrized on other algorithms.
       Whenever feasible, such algorithms are implemented and composed from
       existing building blocks.
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       an appropriate default value is defined by the library.
       The default value should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}

@@

Since meta-estimators require users to construct nested objects,
the decision to implement a meta-estimator
rather than integrate the behavior it implements
into existing estimators classes
is always based on a trade-off between generality and ease of use.
Relating to the example just given,
all \sklearn classifiers are designed to do multiclass classification
and the use of the \texttt{multiclass} module
is only necessary in advanced use cases.
